Members

### 2025-04-15 members.qmd
Initial commit

[Marianne Huebner](https://cstat.msu.edu/people/marianne-huebner-phd-sheher) (chair), Professor of Statistics and Probability at Michigan State University, USA. <https://orcid.org/0000-0002-9694-9231>

@@

[Lara Lusa](https://www.famnit.upr.si/sl/zaposleni-in-sodelavci/lara.lusa/), Professor at the Faculty of Mathematics, Natural Sciences and Information Technologies of the University of Primorska in Koper, Slovenia

@@

**Marianne Huebner** is Professor of the Department of Statistics and Probability and Director of the Center for Statistical Training and Consulting at Michigan State University. After receiving a PhD in Applied Mathematics she held positions at UC Berkeley, the Mathematical Sciences Research Institute in Berkeley, the Mayo Clinic, and the University Medical Center in Hamburg, Germany. She develops and applies statistical models motivated by scientific questions. Her research interests include modeling health outcomes, initial data analyses, and sports and exercise.

@@

**Lara Lusa** is Professor of Statistics at the Faculty of Mathematics, Natural Sciences and Information Technologies of the University of Primorska, Slovenia. After receiving a PhD in Applied Statistics from the University of Florence, she worked at the Italian National Cancer Institute of Milan, at the Institute of Biostatistics and Medical Informatics of the University of Ljubljana and was a visiting fellow at the Biometric Research Branch of the National Cancer Institute in Bethesda. Her current research interests are related to the development and validation of predictive models in bio‐medicine, with particular attention to applications using high‐dimensional data and rare events. She is also interested in statistical programming, design of simulation studies, and teaching statistics. Beside the methodological research in statistics, she is also heavily involved as a statistical consultant to researchers in medicine.

@@

**Carsten Oliver Schmidt** is Professor at the Institute of Community Medicine, University Medicine of Greifswald. He is deputy head of the Department of SHIP/ Clinical-Epidemiological Research and leads the functional division "Quality in the Health Sciences". He is PI of several methods and research quality related projects, and speaker of the methods section of the German Society for Epidemiology. He is responsible for quality management procedures in population based observational health studies, has expertise in data linkage of primary and secondary data including registries, claims data, hospitals, and in the development of research infrastructures. Research topics include research methods, the study of subclinical and clinical disorders, incidental findings.

>>>>

[Marianne Huebner](https://cstat.msu.edu/people/marianne-huebner-phd-sheher) (chair), Professor of Statistics and Probability at Michigan State University, USA.

[Lara Lusa](https://www.famnit.upr.si/sl/zaposleni-in-sodelavci/lara.lusa/),(chair) Professor at the Faculty of Mathematics, Natural Sciences and Information Technologies of the University of Primorska in Koper, Slovenia

@@

@@

**Marianne Huebner** is a professor of the Department of Statistics and Probability and Director of the Center for Statistical Training and Consulting at Michigan State University. After receiving a PhD in Applied Mathematics she held positions at UC Berkeley, the Mathematical Sciences Research Institute in Berkeley, the Mayo Clinic, and the University Medical Center in Hamburg, Germany. She develops and applies statistical models motivated by scientific questions. Her research interests include modeling health outcomes, initial data analyses, and sports and exercise. <https://orcid.org/0000-0002-9694-9231>

@@

**Lara Lusa** is a professor of Statistics at the Faculty of Mathematics, Natural Sciences and Information Technologies of the University of Primorska, Slovenia. After receiving a PhD in Applied Statistics from the University of Florence, she worked at the Italian National Cancer Institute of Milan, at the Institute of Biostatistics and Medical Informatics of the University of Ljubljana and was a visiting fellow at the Biometric Research Branch of the National Cancer Institute in Bethesda. Her current research interests are related to the development and validation of predictive models in bio‐medicine, with particular attention to applications using high‐dimensional data and rare events. She is also interested in statistical programming, design of simulation studies, and teaching statistics. Beside the methodological research in statistics, she is also heavily involved as a statistical consultant to researchers in medicine.

@@

**Carsten Oliver Schmidt** is Professor at the Institute of Community Medicine, University Medicine of Greifswald. He is deputy head of the Department of SHIP/ Clinical-Epidemiological Research and leads the functional division "Quality in the Health Sciences". He is PI of several methods and research quality related projects, and speaker of the methods section of the German Society for Epidemiology. He is responsible for quality management procedures in population based observational health studies, has expertise in data linkage of primary and secondary data including registries, claims data, hospitals, and in the development of research infrastructures. Research topics include research methods, the study of subclinical and clinical disorders, incidental findings. <https://orcid.org/0000-0001-5266-9396>
